---
title: "MergeTwoFiles"
author: "Lindsay Rutter"
date: "1/22/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This script will merge the SRA files from the diabetes.data and add.samp.meta dataframes.

# Read in add.samp.meta file
```{r}
library(dplyr)

add.samp.meta.read <- read.table(file = "E-MTAB-5061.sdrf.txt", sep = "\t")
add.samp.meta <- add.samp.meta.read[2:dim(add.samp.meta.read)[1],]

for (i in 1:39){
colnames(add.samp.meta)[i] <- as.character(add.samp.meta.read[1,i])
}
rownames(add.samp.meta) <- add.samp.meta$`Comment[ENA_RUN]`

add.samp.meta <- data.frame(add.samp.meta, 'name' = rownames(add.samp.meta))
```

# Read in diabetes.data file
```{r}
diabetes.data <- read.csv("new_diabetes_and_cftr.csv")
```

# Check merging columns on SRA are identical 
```{r}
identical(labels(diabetes.data$SRA), labels(add.samp.meta$Comment.ENA_RUN.))
```

# Merge the two files together by SRA
```{r}
(m1 <- merge(add.samp.meta, diabetes.data, by.x = "Comment.ENA_RUN.", by.y = "SRA"))
saveRDS(m1,"m1.Rds")
```

# Take subset of columns from merged data frame
```{r}
m1_sub <- m1 %>% select(Characteristics.organism., Characteristics.organism.part., Characteristics.individual., Characteristics.single.cell.well.quality., Factor.Value.cell.type., Characteristics.sex., Characteristics.age., Characteristics.body.mass.index., Factor.Value.disease., Heterozygous.SNPs, Homozygous.SNPs)
colnames(m1_sub) <- c("Organism", "Organism part", "Individual", "Quality", "Cell", "Sex", "Age", "BMI", "Disease", "Heterozygous.SNP", "Homozygous.SNP")
write.csv(m1_sub, "m1_sub.csv")
```

# Change the semicolon format of Heterozygous.SNP and Homozygous.SNP columns to list format
```{r}
#m1_sub$Homozygous.SNP <- lapply(m1_sub$Homozygous.SNP, function(x){strsplit((as.character(x)), ";")})
#m1_sub$Heterozygous.SNP <- lapply(m1_sub$Heterozygous.SNP, function(x){strsplit((as.character(x)), ";")})
saveRDS(m1_sub, "m1_sub.Rds")
```

